$K$-corrections and filter transformations \\ from the restframe ultraviolet to the near infrared

### 2006-02-16 docs/paper/kcorrect_figures.tex
add
git-svn-id: svn+ssh://howdy.physics.nyu.edu/usr/local/svn/kcorrect/trunk@549 75dff457-8751-0410-ab1a-cd701654ce6b

\clearpage
\stepcounter{thefigs}
\begin{figure}
\figurenum{\fignum}
\plotone{spec_lrg.ps}
\caption{\label{spec_lrg} Best fit LRG spectral template
	(normalization is for a 1 $M_\odot$ galaxy located 10 pc away, or
	equivalently a $10^{12}$ $M_\odot$ galaxy located 10 Mpc away).}
\end{figure}

\clearpage
\stepcounter{thefigs}
\begin{figure}
\figurenum{\fignum}
\plotone{sfh_lrg.ps}
\caption{\label{sfh_lrg} Star-formation history corresponding to LRG
	spectral template of Figure \ref{spec_lrg}. Top panel shows the
	number of stars formed per logarithmic time interval ($t$ is
	expressed in years, curve is normalized for a $10^{12}$ $M_\odot$
	galaxy). Almost all of the stars are formed in the first couple of
	billion years --- note that the recent ``spike'' is represents a
	tiny fraction ($\sim 10^{-8}$) of the total number of stars. Bottom
	panel shows the mean metallicity of the population as a function of
	time.  }
\end{figure}

@@

\clearpage
\stepcounter{thefigs}
\begin{figure}
\figurenum{\fignum}
\plotone{sfh_templates.ps}
\caption{\label{sfh_templates} SDSS colors of LRGs as a function of
	redshift. The greyscale is the conditional distribution of color
	within each redshift bin. The thin lines are the 10\%, 25\%, 50\%,
	75\%, and 90\% quantiles of the distribution. The thick line
	is the prediction of the model. The $u$ band is not included in the
	fit, and the $u$ magnitudes of most LRGs are poorly known. The other
	colors fit the models reasonably well. This model, remember, is
	given incredible freedom, meaning that the above agreement is the
	best one can do with the stellar population synthesis code of
	\citet{bruzual03a}. }
\end{figure}

>>>>

\clearpage
\stepcounter{thefigs}
\begin{figure}
\figurenum{\fignum}
\plotone{spec_lrg.ps}
\caption{\label{spec_lrg} Best fit LRG spectral template in the rest
frame (normalization is for a 1 $M_\odot$ galaxy located 10 pc away,
or equivalently a $10^{12}$ $M_\odot$ galaxy located 10 Mpc away).}
\end{figure}

\clearpage
\stepcounter{thefigs}
\begin{figure}
\figurenum{\fignum}
\plotone{sfh_lrg.ps}
\caption{\label{sfh_lrg} Star-formation history corresponding to LRG
	spectral template of Figure \ref{spec_lrg}. Top panel shows the
	number of stars formed per logarithmic time interval ($t$ is
	expressed in years, curve is normalized for a $10^{12}$ $M_\odot$
	galaxy). Almost all of the stars are formed in the first couple of
	billion years --- note that the recent ``spike'' is represents a
	tiny fraction ($\sim 10^{-8}$) of the total number of stars. Bottom
	panel shows the mean metallicity of the population as a function of
	time. Note that the details of these functions are rather poorly
	constrained. }
\end{figure}

@@

\clearpage
\stepcounter{thefigs}
\begin{figure}
\figurenum{\fignum}
\plotone{sfh_templates.ps}
\caption{\label{sfh_templates} Similar to Figure \ref{sfh_lrg}, but
for the five global templates. Again, there are many degeneracies in
the fit parameters (though there are fewer in the actual spectra), so
these figures need to be interpreted appropriately.}
\end{figure}

### 2006-02-16 docs/paper/kcorrect_tables.tex
add
git-svn-id: svn+ssh://howdy.physics.nyu.edu/usr/local/svn/kcorrect/trunk@549 75dff457-8751-0410-ab1a-cd701654ce6b

\begin{deluxetable}{rrrrr}
\tablewidth{0pt}
\tablecolumns{5}
\tablecaption{\label{solarmagnitudes} Properties of various filters}
\tablehead{ Band & $\lambda_{\mathrm{eff}}$ (\AA) & $m_{\mathrm{AB}} -
	m_{\mathrm{Vega}}$ & $M_\odot$ (AB) &
	$M_\odot$ (Vega)}
\startdata
\input{solarmagnitudes.tex}
\enddata
\tablecomments{Uses model solar spectrum and model Vega spectrum of
	\citet{kurucz91a}. Effective wavelength is defined in the text.}
\end{deluxetable}

\begin{deluxetable}{cc}
\tablewidth{0pt}
\tablecolumns{2}
\tablecaption{\label{lineareqs} Conversions among various filters}
\tablehead{ Equation & Color dispersion }
\startdata
\input{lineareqs.tex}
\enddata
\tablecomments{Uses AB magnitudes throughout.}
\end{deluxetable}

>>>>

\begin{deluxetable}{rrrrr}
\tablewidth{0pt}
\tablecolumns{5}
\tablecaption{\label{solarmagnitudes} Properties of various filters}
\tablehead{ Band & $\lambda_{\mathrm{eff}}$ (\AA) & $m_{\mathrm{AB}} -
	m_{\mathrm{Vega}}$ & $M_\odot$ (AB) &
	$M_\odot$ (Vega)}
\startdata
\input{solarmagnitudes.tex}
\enddata
\tablecomments{Uses model solar spectrum and model Vega spectrum of
	\citet{kurucz91a}. Effective wavelength is defined in the text. The
	$UBRVI$ filters are those of \citet{bessell90a}. The $ugriz$ filters
	are those determined by Mamoru Doi, Daniel Eisenstein, and James
	Gunn and available on the SDSS DR4 web site.\footnote{{\tt
	http://www.sdss.org/dr4/}} The $JHK_s$ filters are those from
	\citet{cohen03a}. }
\end{deluxetable}

\begin{deluxetable}{lr}
\tablewidth{0pt}
\tablecolumns{2}
\tablecaption{\label{lineareqs} Conversions among various filters}
\tablehead{ Equation & Color dispersion }
\startdata
\input{lineareqs.tex}
\enddata
\tablecomments{Uses AB magnitudes throughout.}
\end{deluxetable}

\begin{deluxetable}{llcl}
\tablewidth{0pt}
\tablecolumns{4}
\tablecaption{\label{derived} Header and Data Units (HDUs) of {\tt k\_nmf\_derived.default.fits}}
\tablehead{ Number & Name & Dimensions & Description}
\startdata
0 & {\tt templates} & $N_{\mathrm{basis}} \times N_t$ & Coefficients
in basis space for each template \cr 1 & {\tt spec} &
$N_{\mathrm{spec}} \times N_t$ & Smoothed spectrum of each template
\cr 2 & {\tt spec\_nl} & $N_{\mathrm{spec}} \times N_t$ & Smoothed
spectrum of each template, lines removed \cr 3 & {\tt spec\_nd} &
$N_{\mathrm{spec}} \times N_t$ & Smoothed spectrum of each template,
without dust \cr 4 & {\tt spec\_nl\_nd} & $N_{\mathrm{spec}} \times
N_t$ & Smoothed spectrum of each template, without lines or dust \cr 5
& {\tt rawspec} & $N_{\mathrm{spec}} \times N_t$ & Unsmoothed spectrum
of each template \cr 6 & {\tt rawspec\_nl} & $N_{\mathrm{spec}} \times
N_t$ & Unsmoothed spectrum of each template, lines removed \cr 7 &
{\tt rawspec\_nd} & $N_{\mathrm{spec}} \times N_t$ & Unsmoothed
spectrum of each template, without dust \cr 8 & {\tt rawspec\_nl\_nd}
& $N_{\mathrm{spec}} \times N_t$ & Unsmoothed spectrum of each
template, without lines or dust \cr 9 & {\tt lspec} &
$N_{\mathrm{spec}} \times N_t$ & emission line spectrum \cr 10 & {\tt
extinction} & $N_{\mathrm{spec}} \times N_t$ & extinction as a
function of wavelength \cr 11 & {\tt lambda} & $N_{\mathrm{spec}}$ &
Wavelength grid (\AA) \cr 12 & {\tt sfr} & $N_{\mathrm{age}} \times
N_t$ & Star-formation rate ($M_\odot$ per year) as a function of time
\cr 13 & {\tt metallicity} & $N_{\mathrm{age}} \times N_t$ & Average
metallicity as a function of time \cr 14 & {\tt ages} &
$N_{\mathrm{age}}$ & Age grid (yrs) \cr 15 & {\tt dage} &
$N_{\mathrm{age}}$ & Age bin size (yrs); {\tt sfr}$\times${\tt dage}
$=$ total star-formation in each bin \cr 16 & {\tt mass} & $N_t$ &
total mass formed in each template \cr 17 & {\tt mremain} & $N_t$ &
total current stellar mass in each template \cr 18 & {\tt mets} &
$N_t$ & average metallicity of current stars in each template \cr 19 &
{\tt m300} & $N_t$ & total stellar mass formed in last 300 Myrs in
each template \cr 20 & {\tt m1000} & $N_t$ & total stellar mass formed
in last 1 Gyr in each template \cr 21 & {\tt basis\_ages} &
$N_{\mathrm{age}} \times N_{\mathrm{mets}} \times N_{\mathrm{dust}}$ &
ages of each stellar population basis vector \cr 22 & {\tt
basis\_mets} & $N_{\mathrm{age}} \times N_{\mathrm{mets}} \times
N_{\mathrm{dust}}$ & metallicity of each stellar population basis
vector \cr 23 & {\tt basis\_dusts} & $N_{\mathrm{age}} \times
N_{\mathrm{mets}} \times N_{\mathrm{dust}}$ & dust properties of each
stellar population basis vector \cr 24 & {\tt basis\_mremain} &
$N_{\mathrm{age}} \times N_{\mathrm{mets}} \times N_{\mathrm{dust}}$ &
fraction of original stellar mass surviving for each basis vector \cr
\enddata 
\tablecomments{All quantities are in floating point (four byte)
precision, except {\tt dusts} which is an array of structures, whose
format is described in text.}
\end{deluxetable}
